Review on precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-04 manuscript.tex
Update manuscript.tex
importing from manubot : compiles ! :-O

\begin{figure}
\centering
%\includegraphics[width=1\textwidth,height=\textheight]{https://media.springernature.com/lw685/springer-static/image/art\%3A10.1038\%2Fs41467-021-26175-1/MediaObjects/41467_2021_26175_Fig1_HTML.png}
\caption{a Spike raster for repeated presentations (N = 40) of a high-contrast (10\% Michelson contrast) drifting Gabor recorded from area MT of a fixating marmoset (stimulus-onset, red line; mean response, blue line). A single-trial LFP trace is plotted in gray, and the average LFP response is plotted in black. The relative power between baseline (−200 ms to stimulus-onset) and evoked fluctuations (stimulus-onset + 50--250 ms) significantly favored the evoked response (right panel; N = 110 trials; median = 1.89 dB, p = 0.000019, two-tailed Wilcoxon's ranked-sum test). b Same as in (a), but for a low contrast stimulus (\textless2\% Michelson contrast). The relative power between baseline and evoked LFP fluctuations was not statistically different from parity (median = 1.23 dB, p = 0.087 two-tailed Wilcoxon's ranked-sum test). c An example of spontaneous LFP fluctuations structured as a traveling wave recorded from a spatially distributed multielectrode array in marmoset area MT. d Histogram of spontaneous spike probability as a function of the generalized phase of the LFP during fixation. e The average evoked response to low contrast stimuli was stronger when a more excitable phase (±π rad) of a spontaneous traveling wave aligned with the retinotopic location of the target (aligned, green line) as compared to when a less excitable phase (0 rad) was aligned (unaligned, purple line; N = 43 wave and non-wave trials; shaded region SEM; p = 0.0000015 two-tailed Wilcoxon's rank-sum test). Data for panels c--e modified from Davis et al.17 with permission.}\label{fig:davis}
\end{figure}

@@

\subsubsection{TODO \ldots{} and to synfire braids and polychronous groups}\label{todo-and-to-synfire-braids-and-polychronous-groups}
\begin{itemize}
\tightlist
\item
 ~\citep{ref-HjDb1gnq} : from synfire chains to Synfire braids
\end{itemize}

@@

\subsection{Cortical songs}\label{cortical-songs}
\begin{itemize}
\tightlist
\item
  Ikegaya and colleagues~\citep{ref-Mf6h1KNY} worked on spontaneous activity in vitro and in vivo. They demonstrated that in cortical activity, we can find a repetition of several motifs. In PSCs, but also in spike activity. These sequences repeat after minutes and have a precise spatio temporal structure with a ms precision. They can be specific of a particular layer or colomn, are synchronized with network activity oscillation and can involve several cells. They also demonstated that these sequences can form supersequences : the cortical songs. It consist of the assembly of several sequences which repeat in a specific order with a compressed timing.
\item
  ``We find precise repetitions of spontaneous patterns of synaptic inputs in neocortical neurons in vivo and in vitro. These patterns repeat after minutes, maintaining millisecond accuracy.''
\item
  Precisely repeating motifs of spontaneous synaptic activity in slices: duration around 1s +/- .5 s. Some events in motifs are of similar size but sometimes absent - better described by Bernouilli than SE (and covariance)
\item
  \emph{in vivo} spontaneous activity also reveals repeating sequences. About 3000 sequences, each involving 3-10 cells out of about 900, and last up to 3 seconds
\item
  topography: ``Sequences had specific topographic structures, in some cases involving only a particular layer or a vertical column of cells or cells located in a cluster (Fig. 4, A and B, and fig.~S3B). (\ldots) Therefore, repeating temporal patterns of activation (\ldots) were associated with a structured spatial organization of the neurons that formed them.''
\item
  ``Cortical songs: modular assemblies of repeated sequences'': hierarchical detection.
\item
  in cotical songs, there is a ``compressing timing'' which may be taken into account by a similar mechanism as maxpooling in CNNs for space, but in time. Or there may be a mechanism for controlling the replay speed (pulvinar, \ldots{} , ?)
\end{itemize}

\begin{figure}
\centering
\includegraphics{images/Ikegaya2004zse0150424620001.jpeg}
\caption{Fig. 1. from~\citep{ref-Mf6h1KNY} Repeated motifs of spontaneous synaptic activity in vitro and in vivo. (A) Repeated motifs of intracellular activity from layer 5 pyramidal neurons in slices. Panels show segments (red) of the same voltage-clamp recording from the same cell repeating seconds or minutes after the initial occurrence (blue). Arrows indicate timings of repeated PSCs. (i) Upper trace: low--temporal resolution display of spontaneous activity of a neuron. Lower traces: higher resolution display of the repeated motif at indicated regions of the trace (a to c). (ii) Example of a longer motif. (B) Three repetitions of a motif. The top traces show the motifs superimposed on each other (blue, green, and red), the middle traces show these same traces individually, and the bottom traces show temporally magnified regions of the motifs (a to c). (C) Repeated sequences of intracellular current-clamp recordings in vivo. Two (i) and three (ii) repetitions of motifs are shown. Shuffle tests were performed on traces (i), a to c, yielding significantly fewer repeats (fig.~S2, P \textless{} 0.02). In (i), the blue trace is shifted --2.75 mV; in (ii), the blue trace is shifted --1.58 mV, and the green +0.79 mV.}\label{fig:Ikegaya2004}
\end{figure}

@@

  \begin{itemize}
  \tightlist
  \item
    comes with python code
  \end{itemize}
\item
  blog post by Paxon Frady \url{https://epaxon.blogspot.com/2012/07/izhikevich-2006-polychronization.html}
\item
  dynamic networks \& learning delays:

@@

\begin{itemize}
\tightlist
\item
  https://www.janelia.org/lab/stringer-lab
\item
  described in~\citep{ref-zc16plUu}{100}{]}
\item
  \href{https://github.com/MouseLand/rastermap}{rastermap}
\item
  deconvolution strategy
\item
  based on a linear model
\end{itemize}

\subsubsection{\texorpdfstring{Stringer et al 2019, Nature~\citep{ref-brg2FFsb}{101}{]}}{Stringer et al 2019, Nature {[}101{]}}}\label{stringer-et-al-2019-nature-stringer2019nature}
\begin{itemize}
\tightlist
\item
  ``A neuronal population encodes information most efficiently when its stimulus responses are high-dimensional and uncorrelated, and most robustly when they are lower-dimensional and correlated. Here we analysed the dimensionality of the encoding of natural images by large populations of neurons in the visual cortex of awake mice.''
\item
  Data availability: All of the processed deconvolved calcium traces are available on \href{https://figshare.com/articles/Recordings_of_ten_thousand_neurons_in_visual_cortex_in_response_to_2_800_natural_images/6845348}{figshare}, together with the image stimuli.
\item
  Code availability: The code is available on \href{https://github.com/MouseLand/stringer-pachitariu-et-al-2018b}{GitHub}.
\end{itemize}

@@

\subsection{detecting structured temporal patterns}\label{detecting-structured-temporal-patterns}
\subsubsection{\texorpdfstring{Paper by Grossberger, 2018~\citep{ref-9AK1cwY1}{104}{]}}{Paper by Grossberger, 2018 {[}104{]}}}\label{paper-by-grossberger-2018-grossberger2018}
\begin{itemize}
\tightlist
\item
  Temporally ordered multi-neuron patterns likely encode information in the brain. We introduce an unsupervised method, SPOTDisClust (Spike Pattern Optimal Transport Dissimilarity Clustering), for their detection from high-dimensional neural ensembles. SPOTDisClust measures similarity between two ensemble spike patterns by determining the minimum transport cost of transforming their corresponding normalized cross-correlation matrices into each other (SPOTDis).
\item
  Detecting these temporal patterns represents a major methodological challenge.
\item
  Many approaches to this problem are supervised, that is, they take patterns occurring concurrently with a known event, such as the delivery of a stimulus for sensory neurons or the traversal of a running track for hippocampal place fields, as a ``template'' and then search for repetitions of the same template in spiking activity :
\item
  Nadasdy Z, Hirase H, Czurko A, Csicsvari J, Buzsaki G. Replay and time compression of recurring spike sequences in the hippocampus. J Neurosci. 1999;19(21):9497--507. pmid:10531452
\item
  Lee AK, Wilson MA. A combinatorial method for analyzing sequential firing patterns involving an arbitrary number of neurons based on relative time order. J Neurophysiol. 2004;92(4):2555--73. pmid:15212425
\item
  Davidson TJ, Kloosterman F, Wilson MA. Hippocampal replay of extended experience. Neuron. 2009;63(4):497--507. pmid:19709631
\item
  only one spike per neuron: fig 1A = ``For each pattern and each neuron, a random position was chosen for the activation pulse.''
\item
  t-SNE projection with HDBSCAN labels shows that our clustering method can retrieve all patterns from the data.
\item
  data available @ https://doi.org/10.1371/journal.pcbi.1006283.s013
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  ``However, SPOTDis has two principal weaknesses that we address here: (1) Its computational complexity, for comparing two time epochs, is O(N2), where N is the number of neurons. This becomes a major problem for computing an MM dissimilarity matrix (for M time epochs) for thousands of neurons. (2) It relies exclusively on pairwise spike-timing relationships (i.e 2nd order correlations), because it does not solve the optimal transport problem for the entire spike pattern, but only for neuron pairs separately. Hence, it may not be sensitive to higher-order correlations in spiking
  patterns.
  Here, we develop a novel dissimilarity measure for multi-neuron spiking patterns called SpikeShip, which has linear computational complexity of O(N). We achieve this by (1) computing the minimum transport cost of spikes for each spike train separately, and (2) discounting a global translation term in the transport flow across neurons.''
  https://doi.org/10.1101/2020.06.03.131573;
\end{itemize}

\subsubsection{\texorpdfstring{Paper by Russo et al 2017~\citep{ref-RrgzWOSk}}{Paper by Russo et al 2017 {[}88{]}}}\label{paper-by-russo-et-al-2017-russo2017}
\begin{itemize}
\tightlist
\item
  ``Here we present such a unifying methodological and conceptual framework which detects assembly structure at many different time scales, levels of precision, and with arbitrary internal organization.'' by~\citep{ref-RrgzWOSk}
\item
  sliding window as in~\citep{ref-1XpTamcl}{105}{]} (``Numerous other statistical procedures for detecting assemblies or sequential patterns have been proposed previously'') - extended to multiple lags~\citep{ref-bc9czTxi}
\item
  based on a ``non-stationarity-corrected parametric test statistic for assessing the independence of pairs'' and ``an agglomerative, heuristic clustering algorithm for fusing significant pairs into higher-order assemblies''
\end{itemize}

\subsubsection{\texorpdfstring{Neural Variability and Sampling-Based Probabilistic Representations in the Visual Cortex~\citep{ref-1300cS9RL}{106}{]}}{Neural Variability and Sampling-Based Probabilistic Representations in the Visual Cortex {[}106{]}}}\label{neural-variability-and-sampling-based-probabilistic-representations-in-the-visual-cortex-orban2016}
\begin{itemize}
\tightlist
\item
  Stochastic sampling links perceptual uncertainty to neural response variability
\item
  Model accounts for independent changes in strength and variability of responses
\item
  Model predicts relationship between noise, signal, and spontaneous correlations
\item
  Stimulus statistics dependence of response statistics is explained
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
 ~\citep{ref-11p3NXmkg}{113}{]} : coherence detection
\item
 ~\citep{ref-j5xS3owo}{114}{]} : STDP
\item
  Masquelier, Gilson et al.~- 2010 - STDP in Recurrent Neuronal Networks~\citep{ref-15TktA0gR}{115}{]} or Delay Selection by Spike-Timing-Dependent Plasticity in Recurrent Networks of Spiking Neurons Receiving Oscillatory Inputs. PLoS Comput Biol 9(2): e1002897.~\citep{ref-1FHIKpizQ}{116}{]} which targets at the selective potentiation of recurrent connections with different axonal and dendritic delays during oscillatory activity.
\end{itemize}

@@

  \begin{itemize}
  \tightlist
  \item
    the loss function is the cross entropy (following Bernouilli hypothesis with a GLM where each unit is modelled with a SRM neuron~\citep{ref-14e3BCBii}{126}{]} with recurrent dynamics)
  \item
    sample and measure method to include latent / hidden neurons
  \item
    comes with code https://github.com/EPFL-LCN/pub-bellec-wang-2021-sample-and-measure
  \item
    V1-dataset : The dataset we used was collected by Smith and Kohn {[}49{]} and is publicly available at:
    http://crcns.org/data-sets/vc/pvc-11 - it is in a sense supervised with the input being the movie and the output the spikes recorded.
  \end{itemize}
\end{itemize}

>>>>

\begin{figure}
\centering
%\includegraphics[width=1\textwidth,height=\textheight]{https://media.springernature.com/lw685/springer-static/image/art\%3A10.1038\%2Fs41467-021-26175-1/MediaObjects/41467_2021_26175_Fig1_HTML.png}
\caption{a Spike raster for repeated presentations (%N = 40) of a high-contrast (10\% Michelson contrast) drifting Gabor recorded from area MT of a fixating marmoset (stimulus-onset, red line; mean response, blue line). A single-trial LFP trace is plotted in gray, and the average LFP response is plotted in black. The relative power between baseline (−200 ms to stimulus-onset) and evoked fluctuations (stimulus-onset + 50--250 ms) significantly favored the evoked response (right panel; N = 110 trials; median = 1.89 dB, p = 0.000019, two-tailed Wilcoxon's ranked-sum test). b Same as in (a), but for a low contrast stimulus (2\% Michelson contrast). The relative power between baseline and evoked LFP fluctuations was not statistically different from parity (median = 1.23 dB, p = 0.087 two-tailed Wilcoxon's ranked-sum test). c An example of spontaneous LFP fluctuations structured as a traveling wave recorded from a spatially distributed multielectrode array in marmoset area MT. d Histogram of spontaneous spike probability as a function of the generalized phase of the LFP during fixation. e The average evoked response to low contrast stimuli was stronger when a more excitable phase (+ / - \pi rad) of a spontaneous traveling wave aligned with the retinotopic location of the target (aligned, green line) as compared to when a less excitable phase (0 rad) was aligned (unaligned, purple line; N = 43 wave and non-wave trials; shaded region SEM; p = 0.0000015 two-tailed Wilcoxon's rank-sum test). Data for panels c--e modified from Davis et al.17 with permission.
}\label{fig:davis}
\end{figure}

@@

\subsubsection{TODO \ldots{} and to synfire braids and polychronous groups}\label{todo-and-to-synfire-braids-and-polychronous-groups}
\begin{itemize}
 \item
 ~\citep{ref-HjDb1gnq} : from synfire chains to Synfire braids
\end{itemize}

@@

\subsection{Cortical songs}\label{cortical-songs}
\begin{itemize}
 \item
  Ikegaya and colleagues~\citep{ref-Mf6h1KNY} worked on spontaneous activity in vitro and in vivo. They demonstrated that in cortical activity, we can find a repetition of several motifs. In PSCs, but also in spike activity. These sequences repeat after minutes and have a precise spatio temporal structure with a ms precision. They can be specific of a particular layer or colomn, are synchronized with network activity oscillation and can involve several cells. They also demonstated that these sequences can form supersequences : the cortical songs. It consist of the assembly of several sequences which repeat in a specific order with a compressed timing.
\item
  ``We find precise repetitions of spontaneous patterns of synaptic inputs in neocortical neurons in vivo and in vitro. These patterns repeat after minutes, maintaining millisecond accuracy.''
\item
  Precisely repeating motifs of spontaneous synaptic activity in slices: duration around 1s +/- .5 s. Some events in motifs are of similar size but sometimes absent - better described by Bernouilli than SE (and covariance)
\item
  \emph{in vivo} spontaneous activity also reveals repeating sequences. About 3000 sequences, each involving 3-10 cells out of about 900, and last up to 3 seconds
\item
  topography: ``Sequences had specific topographic structures, in some cases involving only a particular layer or a vertical column of cells or cells located in a cluster (Fig. 4, A and B, and fig.~S3B). (\ldots) Therefore, repeating temporal patterns of activation (\ldots) were associated with a structured spatial organization of the neurons that formed them.''
\item
  ``Cortical songs: modular assemblies of repeated sequences'': hierarchical detection.
\item
  in cotical songs, there is a ``compressing timing'' which may be taken into account by a similar mechanism as maxpooling in CNNs for space, but in time. Or there may be a mechanism for controlling the replay speed (pulvinar, \ldots{} , ?)
\end{itemize}

\begin{figure}
\centering
\includegraphics{images/Ikegaya2004zse0150424620001.jpeg}
\caption{Fig. 1. from~\citep{ref-Mf6h1KNY} Repeated motifs of spontaneous synaptic activity in vitro and in vivo. (A) Repeated motifs of intracellular activity from layer 5 pyramidal neurons in slices. Panels show segments (red) of the same voltage-clamp recording from the same cell repeating seconds or minutes after the initial occurrence (blue). Arrows indicate timings of repeated PSCs. (i) Upper trace: low--temporal resolution display of spontaneous activity of a neuron. Lower traces: higher resolution display of the repeated motif at indicated regions of the trace (a to c). (ii) Example of a longer motif. (B) Three repetitions of a motif. The top traces show the motifs superimposed on each other (blue, green, and red), the middle traces show these same traces individually, and the bottom traces show temporally magnified regions of the motifs (a to c). (C) Repeated sequences of intracellular current-clamp recordings in vivo. Two (i) and three (ii) repetitions of motifs are shown. Shuffle tests were performed on traces (i), a to c, yielding significantly fewer repeats (fig.~S2, P  0.02). In (i), the blue trace is shifted --2.75 mV; in (ii), the blue trace is shifted --1.58 mV, and the green +0.79 mV.}\label{fig:Ikegaya2004}
\end{figure}

@@

  \begin{itemize}
     \item
    comes with python code
  \end{itemize}
\item
  blog post by Paxon Frady \url{https://epaxon.blogspot.com/2012/07/izhikevich-2006-polychronization.html}
\item
  dynamic networks \& learning delays:

@@

\begin{itemize}
 \item
  https://www.janelia.org/lab/stringer-lab
\item
  described in~\citep{ref-zc16plUu}{100}{]}
\item
  \href{https://github.com/MouseLand/rastermap}{rastermap}
\item
  deconvolution strategy
\item
  based on a linear model
\end{itemize}

\subsubsection{\texorpdfstring{Stringer et al 2019, Nature~\citep{ref-brg2FFsb}{101}{]}}{Stringer et al 2019, Nature {[}101{]}}}\label{stringer-et-al-2019-nature-stringer2019nature}
\begin{itemize}
 \item
  ``A neuronal population encodes information most efficiently when its stimulus responses are high-dimensional and uncorrelated, and most robustly when they are lower-dimensional and correlated. Here we analysed the dimensionality of the encoding of natural images by large populations of neurons in the visual cortex of awake mice.''
\item
  Data availability: All of the processed deconvolved calcium traces are available on \href{https://figshare.com/articles/Recordings_of_ten_thousand_neurons_in_visual_cortex_in_response_to_2_800_natural_images/6845348}{figshare}, together with the image stimuli.
\item
  Code availability: The code is available on \href{https://github.com/MouseLand/stringer-pachitariu-et-al-2018b}{GitHub}.
\end{itemize}

@@

\subsection{detecting structured temporal patterns}\label{detecting-structured-temporal-patterns}
\subsubsection{\texorpdfstring{Paper by Grossberger, 2018~\citep{ref-9AK1cwY1}{104}{]}}{Paper by Grossberger, 2018 {[}104{]}}}\label{paper-by-grossberger-2018-grossberger2018}
\begin{itemize}
 \item
  Temporally ordered multi-neuron patterns likely encode information in the brain. We introduce an unsupervised method, SPOTDisClust (Spike Pattern Optimal Transport Dissimilarity Clustering), for their detection from high-dimensional neural ensembles. SPOTDisClust measures similarity between two ensemble spike patterns by determining the minimum transport cost of transforming their corresponding normalized cross-correlation matrices into each other (SPOTDis).
\item
  Detecting these temporal patterns represents a major methodological challenge.
\item
  Many approaches to this problem are supervised, that is, they take patterns occurring concurrently with a known event, such as the delivery of a stimulus for sensory neurons or the traversal of a running track for hippocampal place fields, as a ``template'' and then search for repetitions of the same template in spiking activity :
\item
  Nadasdy Z, Hirase H, Czurko A, Csicsvari J, Buzsaki G. Replay and time compression of recurring spike sequences in the hippocampus. J Neurosci. 1999;19(21):9497--507. pmid:10531452
\item
  Lee AK, Wilson MA. A combinatorial method for analyzing sequential firing patterns involving an arbitrary number of neurons based on relative time order. J Neurophysiol. 2004;92(4):2555--73. pmid:15212425
\item
  Davidson TJ, Kloosterman F, Wilson MA. Hippocampal replay of extended experience. Neuron. 2009;63(4):497--507. pmid:19709631
\item
  only one spike per neuron: fig 1A = ``For each pattern and each neuron, a random position was chosen for the activation pulse.''
\item
  t-SNE projection with HDBSCAN labels shows that our clustering method can retrieve all patterns from the data.
\item
  data available @ https://doi.org/10.1371/journal.pcbi.1006283.s013
\end{itemize}

@@

\begin{itemize}
 \item
  ``However, SPOTDis has two principal weaknesses that we address here: (1) Its computational complexity, for comparing two time epochs, is O(N2), where N is the number of neurons. This becomes a major problem for computing an M dissimilarity matrix (for M time epochs) for thousands of neurons. (2) It relies exclusively on pairwise spike-timing relationships (i.e 2nd order correlations), because it does not solve the optimal transport problem for the entire spike pattern, but only for neuron pairs separately. Hence, it may not be sensitive to higher-order correlations in spiking
  patterns.
  Here, we develop a novel dissimilarity measure for multi-neuron spiking patterns called SpikeShip, which has linear computational complexity of O(N). We achieve this by (1) computing the minimum transport cost of spikes for each spike train separately, and (2) discounting a global translation term in the transport flow across neurons.''
  https://doi.org/10.1101/2020.06.03.131573;
\end{itemize}

\subsubsection{\texorpdfstring{Paper by Russo et al 2017~\citep{ref-RrgzWOSk}}{Paper by Russo et al 2017 {[}88{]}}}\label{paper-by-russo-et-al-2017-russo2017}
\begin{itemize}
 \item
  ``Here we present such a unifying methodological and conceptual framework which detects assembly structure at many different time scales, levels of precision, and with arbitrary internal organization.'' by~\citep{ref-RrgzWOSk}
\item
  sliding window as in~\citep{ref-1XpTamcl}{105}{]} (``Numerous other statistical procedures for detecting assemblies or sequential patterns have been proposed previously'') - extended to multiple lags~\citep{ref-bc9czTxi}
\item
  based on a ``non-stationarity-corrected parametric test statistic for assessing the independence of pairs'' and ``an agglomerative, heuristic clustering algorithm for fusing significant pairs into higher-order assemblies''
\end{itemize}

\subsubsection{\texorpdfstring{Neural Variability and Sampling-Based Probabilistic Representations in the Visual Cortex~\citep{ref-1300cS9RL}{106}{]}}{Neural Variability and Sampling-Based Probabilistic Representations in the Visual Cortex {[}106{]}}}\label{neural-variability-and-sampling-based-probabilistic-representations-in-the-visual-cortex-orban2016}
\begin{itemize}
 \item
  Stochastic sampling links perceptual uncertainty to neural response variability
\item
  Model accounts for independent changes in strength and variability of responses
\item
  Model predicts relationship between noise, signal, and spontaneous correlations
\item
  Stimulus statistics dependence of response statistics is explained
\end{itemize}

@@

\begin{itemize}
 \item
 ~\citep{ref-11p3NXmkg}{113}{]} : coherence detection
\item
 ~\citep{ref-j5xS3owo}{114}{]} : STDP
\item
  Masquelier, Gilson et al.~- 2010 - STDP in Recurrent Neuronal Networks~\citep{ref-15TktA0gR}{115}{]} or Delay Selection by Spike-Timing-Dependent Plasticity in Recurrent Networks of Spiking Neurons Receiving Oscillatory Inputs. PLoS Comput Biol 9(2): e1002897.~\citep{ref-1FHIKpizQ}{116}{]} which targets at the selective potentiation of recurrent connections with different axonal and dendritic delays during oscillatory activity.
\end{itemize}

@@

  \begin{itemize}
     \item
    the loss function is the cross entropy (following Bernouilli hypothesis with a GLM where each unit is modelled with a SRM neuron~\citep{ref-14e3BCBii}{126}{]} with recurrent dynamics)
  \item
    sample and measure method to include latent / hidden neurons
  \item
    comes with code https://github.com/EPFL-LCN/pub-bellec-wang-2021-sample-and-measure
  \item
    V1-dataset : The dataset we used was collected by Smith and Kohn {[}49{]} and is publicly available at:
    http://crcns.org/data-sets/vc/pvc-11 - it is in a sense supervised with the input being the movie and the output the spikes recorded.
  \end{itemize}
\end{itemize}
